DOpElib:\\ Differential Equations and Optimization Environment

### 2013-12-16 Examples/PDE/InstatPDE/Example3/content.tex

>>>>

In addition, this program shows how to change the vector behavior, from our
default option \texttt{fullmem}, where the whole vector
is stored in the computers main memory. Here the storage behavior is set to 
\texttt{store\underline{ }on\underline{ }disc}, where only those unknowns are loaded into 
main memory that are needed in the current time step, while all other 
unknowns are stored on the hard drive.

This behavior is particularly useful, if many time steps are taken; so that the 
whole set of unknowns can no longer be stored in main memory. Note that all vectors 
will allocate the required memory when the vector is reinitialized to a new size.
Hence, for large vectors this may need some time.

To avoid multiple programs accessing the same files on the hard drive, a 
\texttt{lock} file is initialized. Under normal conditions, this will be deleted 
once the program terminates. However, should the program exit exceptionally, the 
lock file will still exist. Calling the program in this case will produce an 
exception, with the following text:
\begin{verbatim}
Warning: During execution of `StateVector<VECTOR>::StateVector` 
         the following Problem occurred!
The directory Results/tmp_state/ is propaply already in use.
\end{verbatim}
To resolve the issue, you have to delete the named directory with the 
temporary storage files manually.
